%This is our Team H dissertation file.
% It only contains a temporary structure of the final report.

\documentclass{l3proj}
\begin{document}
\title{Voice over IP}
\author{Alexandru Danila \\
        Viktor Bakayov \\
        Rhys Simpson \\
        Megan Keane \\
        Ovidiu Popoviciu}
\date{3rd March 2015}
\maketitle
\begin{abstract}

Our abstract which wll be written after finishing the other sections.

What the problem is?\\*
Who cares?\\*
How was it solved?\\*
What follows?\\*


\end{abstract}
\educationalconsent
\tableofcontents
%==============================================================================
\chapter{Introduction}
\label{intro}

This is our introduction. In short, it will contain: (we don't need section headings in here)

Overview\\*

Project description\\*

Motivation\\*

Challenges and work outline\\*


From the structure of our disseration, we followed a waterfall design process.


%==============================================================================
\chapter{Project Requirements}
\label{requirements}

This chapter will contain the requirements for the complete system. We can split them up in 

\section{Requirements gathering}

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

\subsection{Client}

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

\subsection{Server}

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

\subsection{Protocols?}

%------------------------------------------------------------------------------


%==============================================================================
\chapter{Design overview}
\label{design-overview}

This chapter will contain an overview of how everything fits together.

e.g. the control protocol facilitates the connection between the client and the server

the p2p protocol makes voice transmission possible 

and so on


%==============================================================================
\chapter{Client}
\label{client}


\section{Design}

Talk about the different iterations we had, pros and cons of each of the designs. Justify all our design decisions. 

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

\subsection{Functionality}

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

\subsection{User Interface}

%------------------------------------------------------------------------------

\section{Implementation and testing}

%------------------------------------------------------------------------------

\section{Evaluation}

Could we have had a better design? Could it have been more user friendly. Pros and cons of our final product.

%==============================================================================
\chapter{Voice (Peer-to-Peer) Protocol}
\label{p2p}


\section{Design}

%------------------------------------------------------------------------------

\section{Implementation and testing}

%------------------------------------------------------------------------------

\section{Evaluation}


%==============================================================================
\chapter{Control (client-server) Protocol}
\label{tcp}


\section{Design}

%------------------------------------------------------------------------------

\section{Implementation and testing}

%------------------------------------------------------------------------------

\section{Evaluation}


%==============================================================================
\chapter{Server}
\label{server}


\section{Design}

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

\subsection{Functionality}

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

\subsection{Database model}
\label{db}


%------------------------------------------------------------------------------

\section{Implementation and testing}

%------------------------------------------------------------------------------

\section{Evaluation}


%==============================================================================
\chapter{Overall evaluation and future work}

We need both this chapter and different sections for every other component.



An overall review of the project. \\*
Is it functional? \\*
Does our product fulfill our client’s needs and our requirements specification?\\*
If any requirements aren’t met then why? \\*
Was this the best way to design and implement the project?\\*
What would we do differently? \\*
Future plans: if we had more time to work on it what would we do? What improvements would me make?\\*

++++++

Reflection on the overall process \\*

We need to reflect on every component in isolation as well.


%==============================================================================
\chapter{Conclusion}

Success and failures of the process and work as a team.

%==============================================================================
\section{Contributions}

Here we explain what each member of the team contributed to.

For example, Rhys was great at designing the peer-to-peer protocol described in chapter \ref{p2p} and finished quite early.

Alex and Megan worked together on the Client side described in chapter \ref{client} and did a very good job.

Viktor designed and implemented the database described in chapter \ref{server} section \ref{db}.

The TCP protocol described in chapter \ref{tcp} was implemented by Ovidiu.

In the end, through constant communication and coordination, every member of the team participated in 
design of the application and plugging every component into a single whole.

//other contributions bla bla

???

%==============================================================================
\bibliographystyle{plain}
\bibliography{team-h-bib}
\end{document}
